Model Based Systems Engineering with a Docs-as-Code Approach for the SeaLion CubeSat Project

### 2023-04-17 manuscript/template.tex
Add images and change image references file path in template.tex

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/cubesat_family.png}
    \caption{CubeSat family by size \cite{cds_rev14}}
	\label{fig:cubesat_family}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/cubesat_blownup.png}
    \caption{Blownup SeaLion CubeSat Prototype}
	\label{fig:cubesat_blowup}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics{Definitions/impedence.png}
    \caption{Impedence Probe}
	\label{fig:IP}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics{Definitions/spectral.png}
    \caption{Me-S 'Pixel Sensor'}
	\label{fig:Me-S}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/decs.png}
    \caption{DeCS as the black popout booms}
	\label{fig:DeCS}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/launch_data.png}
    \caption{Nanosatellite launch data provided by M. Swartwout as of July 21, 2021 \cite{swartwout_data}}
	\label{fig:launch_data}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/mission_status.png}
    \caption{Mission status of CubeSat university-class missions provided by Swartwout}
	\label{fig:mission_status}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/user_story.png}
    \caption{Example YAML file}
	\label{fig:example_yaml}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics{Definitions/folders.png}
    \caption{Folder structure}
	\label{fig:folders}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/reference.png}
    \caption{References YAML file}
	\label{fig:reference_yaml}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/reference_file.png}
    \caption{References file structure}
	\label{fig:reference_file}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/stakeholder.png}
    \caption{Stakeholder YAML file}
	\label{fig:stakeholder_yaml}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/stakeholder_file.png}
    \caption{Stakeholders file structure}
	\label{fig:stakeholder_file}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/uml_stakeholder.png}
    \caption{Stakeholder UML Diagram}
	\label{fig:uml_stakeholder}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/userstory_file.png}
    \caption{User stories file structure}
	\label{fig:userstory_file}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/view_beacon.png}
    \caption{View Beacon YAML structure}
	\label{fig:view_beacon}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/uml_userstory.png}
    \caption{UML diagram of user stories}
	\label{fig:uml_userstory}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/uml_userstory2.png}
    \caption{UML diagram of ground station operator}
	\label{fig:uml_userstory2}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/datastructure.png}
    \caption{Satellite Health Data Structure}
	\label{fig:datastructure}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/datastructure_file.png}
    \caption{Data structure File Structure}
	\label{fig:datastructure_file}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/uml_datastructure.png}
    \caption{UML Diagram of Data Structures}
	\label{fig:uml_datastructure}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/components_file.png}
    \caption{Components Folder File Structure}
	\label{fig:components_file}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/components.png}
    \caption{Component YAML File}
	\label{fig:components}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{Definitions/N2.png}
    \caption{N2 Chart Example}
	\label{fig:N2}
    \end{figure}   
\unskip

>>>>

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/cubesat_family.png}
    \caption{CubeSat family by size \cite{cds_rev14}}
	\label{fig:cubesat_family}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/cubesat_blownup.png}
    \caption{Blownup SeaLion CubeSat Prototype}
	\label{fig:cubesat_blowup}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics{assets/impedence.png}
    \caption{Impedence Probe}
	\label{fig:IP}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics{assets/spectral.png}
    \caption{Me-S 'Pixel Sensor'}
	\label{fig:Me-S}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/decs.png}
    \caption{DeCS as the black popout booms}
	\label{fig:DeCS}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/launch_data.png}
    \caption{Nanosatellite launch data provided by M. Swartwout as of July 21, 2021 \cite{swartwout_data}}
	\label{fig:launch_data}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/mission_status.png}
    \caption{Mission status of CubeSat university-class missions provided by Swartwout}
	\label{fig:mission_status}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/user_story.png}
    \caption{Example YAML file}
	\label{fig:example_yaml}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics{assets/folders.png}
    \caption{Folder structure}
	\label{fig:folders}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/reference.png}
    \caption{References YAML file}
	\label{fig:reference_yaml}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/reference_file.png}
    \caption{References file structure}
	\label{fig:reference_file}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/stakeholder.png}
    \caption{Stakeholder YAML file}
	\label{fig:stakeholder_yaml}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/stakeholder_file.png}
    \caption{Stakeholders file structure}
	\label{fig:stakeholder_file}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/uml_stakeholder.png}
    \caption{Stakeholder UML Diagram}
	\label{fig:uml_stakeholder}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/userstory_file.png}
    \caption{User stories file structure}
	\label{fig:userstory_file}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/view_beacon.png}
    \caption{View Beacon YAML structure}
	\label{fig:view_beacon}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/uml_userstory.png}
    \caption{UML diagram of user stories}
	\label{fig:uml_userstory}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/uml_userstory2.png}
    \caption{UML diagram of ground station operator}
	\label{fig:uml_userstory2}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/datastructure.png}
    \caption{Satellite Health Data Structure}
	\label{fig:datastructure}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/datastructure_file.png}
    \caption{Data structure File Structure}
	\label{fig:datastructure_file}
    \end{figure}
	\noindent   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/uml_datastructure.png}
    \caption{UML Diagram of Data Structures}
	\label{fig:uml_datastructure}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/components_file.png}
    \caption{Components Folder File Structure}
	\label{fig:components_file}
    \end{figure}   
\unskip

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/components.png}
    \caption{Component YAML File}
	\label{fig:components}
    \end{figure}   
\unskip

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{assets/N2.png}
    \caption{N2 Chart Example}
	\label{fig:N2}
    \end{figure}   
\unskip
